---
title: "Effects of Diagram Standards on Students' Monitoring Accuracy and Text Comprehension - Printed Summary of Analyses for Study 1 and 2"
author: "Sophia"
date: '`r Sys.Date()`'
output: 
  rmdformats::html_clean
---

```{r setup, include=FALSE}

## !! COLLAPSE ALL LINES TO BETTER NAVIGATE THIS SCRIPT !!
## (Edit->Folding->Collapse All / alt+cmd+o/ Ctrl+Alt+o)

knitr::opts_chunk$set(echo = FALSE) # To not print code anywhere

```

```{r source analysis script study 1, include=FALSE}
## Source script of performance data analysis/Study 1
source("Scripts/Scripts_Data_Analyses/Analysis_Gorilla_Performance_Data_Study_1-2.R", local = knitr::knit_global())
# (Source the scrips in two different chuncks to get proper status notifications while knitting)
```

```{r source analysis script study 2, include=FALSE}
## Source script of eye-tracking analysis/Study 2
source("Scripts/Scripts_Data_Analyses/Analysis_Eye_Tracking_Data.R", local = knitr::knit_global())
```
  
# Study 1 - Methods

## Participants, Design, Time On Task & Inter-Rater-Reliability of Measures

```{r descriptives and irr study 1, echo=FALSE, message=FALSE}
desc_age_sample_exp_1_n_80

n_gender_sample_exp_1_n_80

desc_age_sample_exp_1_n_79

n_gender_sample_exp_1_n_79

desc_conditions

all_IRRs
```
  
  
# Study 1 - Results
## *Descriptives Statistics*
```{r result descriptives study 1, include=TRUE, echo=FALSE, message=FALSE}
## Print all descriptives per pooled factor
desc_pooled_factors

jols_below_equal_one_study_1_perc <- unname(jols_below_equal_one_study_1_perc)
  
```
  
`r jols_below_equal_one_study_1_perc`% of participants' judgements of learning differed ≤ 1 point from their actual test scores (i.e., absolute monitoring accuracy ≤ 1 in `r jols_below_equal_one_study_1_perc`% of the cases).


## *Monitoring Accuracy*
  
### *With Pooled Factors as Predictors*  

```{r ML analyses MA pooled factors exp1, echo=FALSE, message=FALSE}
abs_MA_models
```

The model with the interaction `r  p_model_comparison_MA_pooled_fac[1]` significantly more variance compared to the model fitting only main effects `r p_model_comparison_MA_pooled_fac[2]`.  

### *With Conditions as Predictors*
```{r ML analyses MA conditions exp1, echo=FALSE, message=FALSE}
abs_mon_acc_conditions_mod
```

### *Pairwise Comparisons* 
```{r pairwise comparisons MA exp1, echo=FALSE, message=FALSE}
## Absolute Monitoring Accuracy
emm_MA
```

## *Relative Monitoring Accuracy*
```{r ML analyses relative MA pooled factors exp1, echo=FALSE, message=FALSE}
rel_acc_models
```
The model with the interaction `r  p_model_comparison_rel_MA[1]` significantly more variance compared to the model fitting only main effects _p_ `r p_model_comparison_rel_MA[2]`. 

## *Text Comprehension* 
### *With Pooled Factors as Predictors*
```{r ML analyses TC pooled factors exp1, echo=FALSE, message=FALSE}
test_models
```

The model with the interaction `r  p_model_comparison_test_pooled_fac[1]` significantly more variance compared to the model fitting only main effects `r p_model_comparison_test_pooled_fac[2]`.  

### *With Conditions as Predictors*
```{r ML analyses TC conditions exp1, echo=FALSE, message=FALSE}
test_conditions_mod
```

### *Pairwise comparisons* 
```{r pairwise comparisons TC exp1, echo=FALSE, message=FALSE}
emm_test
```

## *Judgements of Learning*
```{r JOL analysis, echo=FALSE, message=FALSE}
## Multilevel model
jol_tab_model

## Interaction Plot 
jol_interaction_plot
```
The model with the interaction `r  p_jol_model_comparison[1]` significantly more variance compared to the model fitting only main effects `r p_jol_model_comparison[2]`. 

### *Pairwise Comparisons*
```{r JOL pairwise comparisons, echo=FALSE, message=FALSE}
emm_JOL
```

```{r eye-tracking analysis article 1, include=FALSE}
#source("Scripts/Scripts_DataAnalyses/DataAnalysis-EyeTrackingData.R", local = knitr::knit_global())

# or sys.source("your-script.R", envir = knitr::knit_global())
```

# Study 2 - Methods

##  Participants, Data Exclusion, Inter-Rate-Reliabilities & Reported Gaze Deviation

```{r Participants, Data Exclusion and Measures exp2, echo=FALSE, message=FALSE}
## Sample Descriptives
desc_age_sample_study_2
n_gender_sample_study_2

## Exclusion of Data
exclusion_overview

## IRR for segments
all_segment_IRRs %>% footnote(general = kappas_coded_segments, general_title = "")

```
  \

Accuracy reported by the eye-tracker software was *M* = `r mean_accuracy_eye_tracker$Mean` (`r mean_accuracy_eye_tracker$SD`).  \
    
# Study 2 - Results
## *Descriptives Fixations*
```{r Descriptives Fixations Cue+Diagram Types, echo=FALSE, message=FALSE}
## Fixation Durations Single Boxes, Per Cue Type, Percent 
fixation_descriptives 

## Little word count table
word_count_table_kbl
```

Participants wrote on average `r word_count_table$Mean[grepl("Own", word_count_table$Diagram_Type)] - word_count_table$Mean[grepl("Standard", word_count_table$Diagram_Type)]` words more in a box of their own diagram compared to words in a box of the standard.


## *Analysis Fixation Durations* 
```{r ML average fixation durations, echo=FALSE, message=FALSE}
# Fixation Durations Single Boxes, Per Cue Type in seconds
fixation_duration_output
```

### *Pairwise comparisons*
```{r pairwise comparisons fixation durations, echo=FALSE, message=FALSE}
# Pairwise comparisons average fixation durations
fixation_duration_mod_emm 
```

## *Transition Table* 
```{r transition table of fixations, echo=FALSE, message=FALSE}
transition_frame_2_print
```

Participants made between `r desc_transitions$Min` and `r desc_transitions$Max` fixation transitions throughout the study, ( _M_  = `r desc_transitions$Mean`, _SD_ = `r gsub("[()]", "", desc_transitions$SD)`).

## *Cued Retrospective Verbal Reports*
```{r table of coded segments-utterances, echo=FALSE, message=FALSE}
## Table Cued-Retrospective Reports
segment_summary
```

The total number of coded segments was `r as.numeric(total_n_segments)`, with `r as.numeric(total_jol_segments)` voiced during the JOL screen.

## *Cue Values, Cue Diagnosticity and Cue Utilization* 
### *Study 1 and 2*
```{r Cue Values Diagnosticity Utilization , echo=FALSE, message=FALSE}
desc_Cues
```
### *Differences between conditions of Study 1*
```{r test differences of cue values etc between conditions of Exp1, echo=FALSE, message=FALSE}
cue_value_summary_study_1
cue_diag_summary_study_1
cue_util_summary_study_1
```
For completeness: the adjusted p-values for multiple testing for the cue values were `r cue_values_study_1_adjusted_p` and for the cue diagnosticities and cue utilizations `r cue_corrs_adjusted_p_study_1`.


### *Differences between Study 1 and 2*
```{r test differences of cue values etc between experiments, echo=FALSE, message=FALSE}
cue_value_summary
cue_diag_summary
cue_util_summary
```
For completeness: the adjusted p-values for multiple testing for the cue values were `r cue_values_adjusted_p` and for the cue diagnosticities and cue utilizations `r cue_corrs_adjusted_p`.

...

